Automated verification of stand-alone solar photovoltaic systems

### 2018-11-21 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
paper update

% incremental ESBMC text here
Related to the standardized input language to SMT solvers, aka SMTLIB logic format, there is a resource called \textit{assertion stack}. An assertion, in SMT solvers, is a constraint on the variables in formula that must hold if the formula is satisfiable \cite{Morse2015}. New assertions can be added to or old assertions removed from this stack, depending on the evaluated value of variables. This enables the solver to learn from previous checks for future checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and discart data during the process, incrementally. This technique is called "Incremental SMT" \cite{Morse2015}. The process of retraction to build and deconstruct the formula allow reduced SMT-conversion overhead of memory, mainly when the verified system is complex and the computing platform do not have large amount of RAM memory to deal with all the design space state.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
%%%%%ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way. 
%
%ESBMC aims to support all of ISO/IEC 9899:2017 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs. Classes of problems that can be detected include: user specified assertion failures, out of bounds array access, illegal pointer dereferences, double-free of malloc'd memory, misaligned memory access; integer overflows, divide by zero, memory leaks, concurrent software, deadlock, and data races (i.e. competing writes).

@@

%------------------------------------------
\subsection{Objectives and Setup}
%------------------------------------------

Our experimental evaluation aims to answer three research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
\end{enumerate}

@@

All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{At the terminal, the command used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

@@

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
We have evaluated five case studies in total. Related to the results of the automated verification and the evaluation if the results are correct: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

We evaluated the same five case studies using HOMER Pro tool. The result of simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed with HOMER Pro.

Despite the divergence of results for the house 1, comparing our automated tool with HOMER Pro, it is evident that the information collect from the dweller shows that the automated verification has the correct evaluation of the PV system. House 5 presented flaws from both tools, however only the automated verification showed which system project error was responsible for the flaw (the cause was the number of solar panels in parallel). However, houses 2, 3 and 4 did not have results from the verification tool, considering the established time-out for the experimental evaluation.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

@@

\textit{Time step:} The runtime complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.

@@

%-------------------------------------
\section{Conclusion and Future Work}
\label{sec:Conclusions}
%-------------------------------------
We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W. Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools. In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail. New tests must be performed, in an improved setup (i.e., better computing performance), aiming to obtain the results from the houses that presented time-out condition. As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems. We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.
%
%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results. The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

@@

% use section* for acknowledgment
\section*{Acknowledgment}
The authors would like to thank Newton Fund (Star Energy project), Coventry University, Sustainable Amazonas Foundation (FAS), and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support and for the possibility to test the tool with real PV systems.

>>>>

% incremental ESBMC text here
Related to the standardized input language to SMT solvers (SMTLIB logic format), there is a resource called \textit{assertion stack}. An assertion, in SMT solvers, is a constraint on the variables in formula that must hold if the formula is satisfiable \cite{Morse2015}. New assertions can be added to or old assertions removed from this stack, depending on the evaluated value of variables. This enables the solver to learn from previous checks, optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and discart data during the process, incrementally. This technique is called "Incremental SMT" \cite{Morse2015}. The process of retraction to build and deconstruct the formula allow to reduce the overhead of memory, mainly when the verified system is complex and the computing platform do not have large amount of memory to deal with all the design space state.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5%
%%%%%ESBMC can be invoked through the command-line interface or configured through the Eclipse plug-in. Specific problems and the solver can be selected that way. 
%
%ESBMC aims to support all of ISO/IEC 9899:2017 C programming language standard, and detects errors in software by simulating a finite prefix of the program execution with all possible inputs. Classes of problems that can be detected include: user specified assertion failures, out of bounds array access, illegal pointer dereferences, double-free of malloc'd memory, misaligned memory access; integer overflows, divide by zero, memory leaks, concurrent software, deadlock, and data races (i.e. competing writes).

@@

%------------------------------------------
\subsection{Objectives and Setup}
%------------------------------------------
Our experimental evaluation aims to answer three research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
\end{enumerate}

@@

All experiments were conducted on an otherwise idle Intel Core i7-2600 (8-cores), with 3.4 GHz and 64 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning our verification engine, ESBMC v5.1 was used with the SMT incremental mode\footnote{At the terminal, the command used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}. The experiments were performed without a predefined timeout.

@@

%------------------------------------------
\subsection{Results}
\label{sec:results_indeed}
%------------------------------------------
%
%\textcolor{red}{We should answer the two research questions here... please take a look at https://ssvlab.github.io/lucasccordeiro/papers/cav2017.pdf to check how you can answer.}
%\begin{enumerate}
%\item[RQ1] \textbf{(soundness)} Does our approach provide correct results?
%\item[RQ2] \textbf{(performance)} How does our approach compare against other existing tools?
%
We have evaluated five case studies in total. Related to the results of the automated verification and the evaluation if the results are correct: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 PV panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems of houses 1, 2, 3, and 4, the sizing check was successful during automated verification, but there was found flaws related with the battery autonomy, when SOC reached a empty-battery level. The automated verification identified the flaws (for all houses) right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this flaw at house 1; 611.2 hours to house 2; 615.8 hours to house 3, and 620.8 hours to house 4. This possible flaws were confirmed with the dwellers that owns the systems by interview: at least once a mouth is usual the system to turn off, normally in raining or clouds days, reaching the situation described in Step 3 of \ref{table:controller}; and after the sun rises, the systems returns to normal operation.

The same five case studies were evaluated by HOMER Pro. The result of simulation shows that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed with HOMER Pro.

Despite the divergence of results for the houses 1, 2, 3 and 4, comparing our automated tool with HOMER Pro, it is evident that the information collect from the dweller shows that the automated verification has the correct evaluation of the PV system. House 5 presented flaws from both tools, however only the automated verification showed which system project error was responsible for the flaw (number of PV panels).

It is worth to mention that a PV design always uses daily average values of sun hours to each site, with impact at the PV components. Those hours are based on historic data and, in field, it is not unusual to find days where that number of hours was not reached, because of weather. The season has impact, as the fact that the case studies are from the Rain Forest, where the clouds are always present. With that in mind, the identified flaws at houses 1, 2, 3, and 4, are justified once again.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

@@

\textit{Time step:} The run-time complexity of our proposed method is an issue; the time step of one hour can be further reduced to approximate the algorithm to the real-world scenario, where a solar irradiance and ambient temperature can change in fractions of minutes.

@@

%-------------------------------------
\section{Conclusion and Future Work}
\label{sec:Conclusions}
%-------------------------------------
We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W. Although this verification method takes longer than simulation tools, it is able to find specific conditions that lead to failures in a PV system previously validated by simulation tools. In particular, the proposed method was successful in finding sizing errors and indicating in which conditions a PV system can fail. New tests must be performed, in an improved setup (i.e., better computing performance), aiming to obtain the results in less time. As future work, the proposed method will be extended to start from a list of commercial equipment, where each equipment is verified and the final solution, which satisfies the project specification, is found via Counterexample Guided-Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}, thus leading to an optimum sizing of PV systems. We also will consider other types of renewable energy and even hybrid ones, which will allow our method to design and verify typical rural electrification.
%
%It was shown that, although the time-consuming issue of the proposed automated verification tool, it overcomes the results of off-the-shelf tool that only simulate the results. The proposed tool was successful in find sizing errors and to indicate in which conditions a PV system can fails.
% into an important instrument to complement the solar PV system design process, ensuring that it does not fail and meets the expected requirements.

@@

% use section* for acknowledgment
\section*{Acknowledgment}
To Coventry University and Sustainable Amazonas Foundation (FAS) for the possibility to test real PV systems.
